Appendix A

### 2024-02-29 manuscript/Appendix A.qmd
methods draft complete

---
title: Appendix A
subtitle: For the article 'Using spatially biased variables in ecosystem condition accounting with a GIS based workflow'
author:
  - name: Anders Lorentzen Kolstad
    email: anders.kolstad@nina.no
    orchid: https://orcid.org/0000-0002-9623-9491
    affiliations: 
        - id: nina
          name: Norwegian Institute for Nature Research
          department: Department of Terrestrial Ecology
          address: Pb 5685 Torgarden
          city: Trondheim
          postal-code: 7485
  - name: Matthew Grainger
    email: matthew.grainger@nina.no
    orchid: https://orcid.org/0000-0001-8426-6495
    affiliations:
        - ref: nina
date: last-modified
format:
  pdf
editor: 
  markdown: 
    wrap: sentence
crossref:
  fig-title: |
    Figure S
  tbl-prefix: Fig S.
  fig-prefix: Fig S.
  tbl-title: |
    Table S
execute:
  echo: false
---

```{r fig-studyLocations}
#| fig.cap: "Position of the three example municiaplieies in Norway."
#| out.width: '50%'

```{r fig-studyLocations}
#| fig.cap: "Barplot showing the total area from each homogeneous impact area 
#| in three Norwegian municipalities"
#| out.width: '50%'

@@

>>>>

---
title: Appendix A
subtitle: For the article 'Horizontal aggregation of spatially biased ecosystem condition indicators – a GIS based workflow'
author:
  - name: Anders Lorentzen Kolstad
    email: anders.kolstad@nina.no
    orchid: https://orcid.org/0000-0002-9623-9491
    affiliations: 
        - id: nina
          name: Norwegian Institute for Nature Research
          department: Department of Terrestrial Ecology
          address: Pb 5685 Torgarden
          city: Trondheim
          postal-code: 7485
  - name: Matthew Grainger
    email: matthew.grainger@nina.no
    orchid: https://orcid.org/0000-0001-8426-6495
    affiliations:
        - ref: nina
  - name: Marianne Evju
    email: marianne.evju@nina.no
    orchid: https://orcid.org/0000-0001-7338-5376
    affiliations:
        - id: nina2
          name: Norwegian Institute for Nature Research
          department: NINA Oslo
          address: Sognsveien 68
          city: Oslo
          postal-code: NO-0855
date: last-modified
format:
  pdf
editor: 
  markdown: 
    wrap: sentence
crossref:
  fig-title: |
    Figure S
  tbl-prefix: Fig S.
  fig-prefix: Fig S.
  tbl-title: |
    Table S
execute:
  echo: false
---

```{r fig-workflow}
#| eval: true
#| include: true
#| out.width: '90%'
#| fig.cap:
#| - "Schematic workflow followed in this paper. ADSV = Anthropogenic Disturbance to Soil and Vegetation."

knitr::include_graphics("../images/workflow.jpg")
```

@@

```{r fig-muniPosition}
#| fig.cap: "Position of the three example municiaplieies in Norway."
#| out.width: '50%'

```{r fig-muniHIAs}
#| fig.cap: "Barplot showing the total area from each homogeneous impact area 
#| in three Norwegian municipalities"
#| out.width: '50%'
